Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Correct a misspelled reference label.

Regularisation is often performed by assuming that species fall into groups, such that all species in the same group interact with other species in the same fashion, thereby collapsing interaction parameters for all the species in that group into one parameter \parencite{ovaskainen2017species,weiss2021disentangling}.
Such groups have been defined \emph{a priori}, by phylogeny at some taxonomic level, or by functional groupings \parencite{uriate2004spatially,ovaskainen2017species,weiss2021disentangling}.
The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
However, tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
While attempts have been made to define functional groups more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, applying these to species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models.

>>>>

Regularisation is often performed by assuming that species fall into groups, such that all species in the same group interact with other species in the same fashion, thereby collapsing interaction parameters for all the species in that group into one parameter \parencite{ovaskainen2017species,weiss2021disentangling}.
Such groups have been defined \emph{a priori}, by phylogeny at some taxonomic level, or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
However, tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
While attempts have been made to define functional groups more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, applying these to species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models.
